Demo: Programming Distributed Control Planes

### 2017-05-15 paper/abstraction/paper.tex

We use \sysname for a range of real-world topologies and routing policies. We find that it can effectively encode the topologies and their evolution, and the fault tolerance bounds that it computes are often precise. 
We also find that \sysname scales substantially better than its nearest competitor, the original \Propane system, 
which operates over concrete topologies. As the number of devices in a
network grows, the number of distinct roles will often stay constant~\cite{surgery}.
Consequently, \sysname can be two orders of magnitude
faster than \Propane, taking less than 10 seconds to synthesize templates for large  networks.

@@

\para{Network verification}
A complementary approach to reducing configuration errors is to analyze the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,surgery,coalgebraic}. Our focus, in contrast, is on a correct-by-construction approach. It has the downside that operators must express policies in a new language, but it saves them from the challenging and time-consuming task of manual configuration generation.

>>>>

We use \sysname for a range of real-world topologies and routing policies. We find that it can effectively encode the topologies and their evolution, and the fault tolerance bounds that it computes are often precise. 
We also find that \sysname scales substantially better than its nearest competitor, the original \Propane system, 
which operates over concrete topologies. As the number of devices in a
network grows, the number of distinct roles will often stay constant.
Consequently, \sysname can be two orders of magnitude
faster than \Propane, taking less than 10 seconds to synthesize templates for large  networks.

@@

\para{Network verification}
A complementary approach to reducing configuration errors is to analyze the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,batfish,bagpipe,arc,era,coalgebraic}. Our focus, in contrast, is on a correct-by-construction approach. It has the downside that operators must express policies in a new language, but it saves them from the challenging and time-consuming task of manual configuration generation.

### 2017-05-15 paper/propane/SOSR/sosr.tex

%\conferenceinfo{SOSR'17,}{April 3--4, 2017, Santa Clara, CA.} 
%\copyrightetc{\copyright~2017 ACM. ISBN \the\acmcopyr}
%\crdata{xxx.\\
%DOI: http://dx.doi.org/10.1145/XXX.XXXXXXX}
%% Update the XXX's to the DOI assigned by ACM rightsreview forms
%\clubpenalty=10000 
%\widowpenalty = 10000

@@

\category{C.2.3}{Computer-Communication Networks}{Network Operations}
\category{D.2.2}{Software Engineering}{Design Tools and Techniques}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003033.10003083.10003098</concept_id>
<concept_desc>Networks~Network manageability</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003099.10003104</concept_id>
<concept_desc>Networks~Network management</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003068.10003073.10003075</concept_id>
<concept_desc>Networks~Network control algorithms</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011050.10011017</concept_id>
<concept_desc>Software and its engineering~Domain specific languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Networks~Network manageability}
\ccsdesc[500]{Networks~Network management}
\ccsdesc[300]{Networks~Network control algorithms}
\ccsdesc[500]{Software and its engineering~Domain specific languages}

>>>>

@@

%\category{C.2.3}{Computer-Communication Networks}{Network Operations}
%\category{D.2.2}{Software Engineering}{Design Tools and Techniques}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003033.10003083.10003098</concept_id>
<concept_desc>Networks~Network manageability</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003099.10003104</concept_id>
<concept_desc>Networks~Network management</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003068.10003073.10003075</concept_id>
<concept_desc>Networks~Network control algorithms</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011050.10011017</concept_id>
<concept_desc>Software and its engineering~Domain specific languages</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{Networks~Network manageability}
\ccsdesc[300]{Networks~Network management}
\ccsdesc[300]{Networks~Network control algorithms}
\ccsdesc[300]{Software and its engineering~Domain specific languages}

\printccsdesc
